\bf Supplement to ``On Devon Allen's Disqualification at the 2022 World Track and Field Championships''

### 2024-11-29 Manuscript/supp.tex
Wrapping up women's section

The results are slightly different from those from the men's data,
which echoes existing studies reporting gender differences in RTs 
\citep[e.g.,][]{lipps2011implications, babicc2009reaction,
  panoutsakopoulos2020gender}.

\of{Currently cannot fit the gg3b to the men's and womens data}

>>>>

We examined several models in the generalized Gamma model and found that the
best model for women involved a venue effect in $\mu$ and heat effect in
$\sigma$.  Thus the best model for men was also the best model for women.

\begin{table}
  \centering
  \caption{Estimated fixed-effect parameters with standard errors in
    parentheses and estimated variance of the random effects from the men's and
    women's fitted GG distribution with venue level random
    effects in $\mu$ and heat level random effects in $\sigma$. $n$ denotes
    size of the data.}
  \label{tab:womensfit}
  \begin{tabular}{c c c c c c c}
    \toprule
    Dataset & $n$ & $\beta_0$ & $\gamma_0$ & $\nu$ & $\tau_v$ & $\tau_h$ \\
    \midrule
    Women's & 732 & $-$1.921 (0.007) & $-$2.071 (0.028) & $-$3.691 (0.665) & 0.057 & 0.111 \\
    Men's & 776 & $-$1.910 (0.005) & $-$2.200 (0.027) & $-$1.178 (0.447) & 0.058 & 0.320 \\
    \bottomrule
  \end{tabular}
\end{table}

One of the most interesting aspects of Table~\ref{tab:womensfit} is that while
the venue effect standard deviation is nearly identical, the women's heat effect
standard deviation is smaller and $\nu$ is much larger.  If men's races have
more variability in times, it seems possible that in men's races that faster
athletes can influence other athletes to react faster in certain instances.
It is also interesting that the standard deviation of the venue effect is
nearly identical for both men's and women's data, indicating that the venue
effect is not only statistically significant but is consistent in strength
across men and women.

We can repeat the simulation methods described in the main paper to evaluate
the probability of an extreme reaction time.  Table~\ref{tab:Sim_prob_women}
compares the men's and women's results of observing reaction times less than
0.08, 0.09, and 0.1 seconds.  We find that across all three comparisons that
women have a lower probability of having a fast time. The results are slightly
different from those from the men's data, which echoes existing studies
reporting gender differences in RTs \citep[e.g.,][]{lipps2011implications,
babicc2009reaction, panoutsakopoulos2020gender}.

\begin{table}
  \centering
  \caption{Probabilities of observing RTs less than threshold 0.08,
  0.09, and 0.10 seconds based on the men's and women's
    fitted GG GAMLSS model with both venue- and heat-level
random effects.}
  \begin{tabular}{c c c c}
   \toprule
   Data Set & Threshold 0.08 & Threshold 0.09 & Threshold 0.10  \\
   \midrule
   Women's & $1\cdot10^{-7}$ & $1.12\cdot10^{-5}$ &  $5.46\cdot10^{-4}$  \\
   Men's   & $6.84\cdot10^{-5}$ & $4.95\cdot10^{-4}$ & $2.76\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_prob_women}
\end{table}

Now we need to perform alter the interpretation of the analyis to determine
what a fair reaction time barrier for women should be.
Table~\ref{tab:Sim_time_women} shows the difference in men's and women's
suggested reaction time barrier.  What we see is that by World Athletics setting
the same standard for men and women, their rules are not fair, in that men are
more likely to be disqualified because they are more likely to react quickly.
One of the biggest takeaways of the reaction time barrier analysis is that the
current standards imposed by World Athletics are not grounded in statistical
analysis and that they should be.  It seems reasonable to either raise the
women's barrier so that they are disqualified at a similar rate as men or to
lower the men's barrier so they are disqualified at a similar rate as women.  But
having equal but not neccessarily fair standards does not seem reasonable when
this study's results echoed results of numerous other papers asking World
Athletics to change the standards.

\begin{table}
  \centering
  \caption{Suggested RT barriers based on tail probabilities.}
  \begin{tabular}{c c c c}
   \toprule
   Data Set & Tail probability  $10^{-2}$ & Tail probability  $10^{-3}$ & Tail probability $10^{-4}$ \\
   \midrule
   Women's & $0.111$ & $0.102$ & $0.095$ \\
   Men's   & $0.108$ & $0.094$ & $0.082$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time_women}
\end{table}
